Cooperation Is Provably Required in a Version of the Noisy Iterated Prisoner's Dilemma

### 2020-05-21 paper/paper.tex
some more work

\begin{definition}
  \label{payofftimeaverage}
  The payoff that $s_1$ gets when playing against $s_2$ is
  \begin{equation*}
    v_{s_1}(s_2) = \sum_{(c_1,c_2)} \pi_{c_1,c_2} \cdot r(G_{s_1}(c_1),G_{s_2}(c_2))
  \end{equation*}
  where $G_s(c)$ is the output of strategy $s$ at state $c$. The sum is taken over all states $(c_1,c_2)$ in the $s_1$-$s_2$ Markov chain.
\end{definition}

For notational convenience, we may also make $r(G_{s_1}(c_1),G_{s_2}(c_2))$ into a vector, denoted by $r$, and write this as the dot product \begin{equation*}
  v_{s_1}(s_2) = \pi \cdot r.
\end{equation*}

@@

We can now state our results! Together, the following two conjectures imply that in the setup described here, mutual cooperation arises as the only stable choice.

\begin{conjecture}
  \label{evolutionarystable1}
  Suppose that a strategy $s_1$ is evolutionarily stable. Then $\lim_{p \to 0} v_{s_1}(s_1) = R$.
\end{conjecture}

\begin{conjecture}
  \label{pavlovtheorem}
  Suppose $2R > T + P$. Then, the Pavlov strategy, depicted in \cref{pavlovfigure}, is evolutionarily stable.
\end{conjecture}

\begin{figure}
  \label{pavlovfigure}
\begin{tikzpicture}[node distance=2cm]
  \node[state,initial] (s_0) {$C$};
  \node[state] (s_1) [right of=s_0] {$D$};

  \path[->] (s_0) edge [loop above] node {$C$} ();
  \path[->] (s_0) edge [bend left] node [above] {$D$} (s_1);
  \path[->] (s_1) edge [loop above] node {$C$} ();
  \path[->] (s_1) edge [bend left] node [below] {$D$} (s_0);
\end{tikzpicture}
  \centering
  \caption{The Pavlov strategy. Similar to but not the same as the Tit-for-tat strategy.}
\end{figure}

@@

\begin{lemma}
  \label{timeaverageisstationary}
  The time average distribution $\pi^{(a,b)}$, for any starting state $(a,b)$, is a stationary distribution of the Markov chain.
\end{lemma}

@@

\begin{lemma}
  An absorbing strongly connected component has a unique time average distribution, i.e., the time average distribution does not depend on the start state.
\end{lemma}

\begin{lemma}
  \label{timeaveragedistributiondecomposition}
  Let $\mathcal{S}$ be the set of absorbing strongly connected components of the $s_1$-$s_2$ Markov chain. For every $C \in \mathcal{S}$, let $\pi^{(C)}$ be its unique time average distribution. Then, for some probabilities $p_C$ with $\sum_{C \in \mathcal{S}} p_C = 1$, depending only on the condensation of the Markov chain, we have \begin{equation*}
    \pi = \sum_{C \in \mathcal{S}} p_C \cdot \pi^{(C)}.
  \end{equation*}
\end{lemma}

@@

\begin{lemma}
  \label{absorbingstronglyconnectedcomponentscartesianproduct}
  Let $\mathcal{C}_1$ be the set of absorbing SCCs of $s_1$, and similarly, let $\mathcal{C}_2$ be the set of absorbing SCCs of $s_2$. If $\mathcal{C}$ is the set of absorbing SCCs of the $s_1$-$s_2$ Markov chain, then it is the cartesian product of the two, i.e.,
  \begin{equation*}
    \mathcal{C} = \mathcal{C}_1 \times \mathcal{C}_2.
  \end{equation*}
\end{lemma}

@@

\begin{lemma}
  \label{neverbetterthanr}
  For any strategy $s$,
  \begin{equation*}
    v_{s}(s) \leq R
  \end{equation*}
\end{lemma}
\begin{proof}
  For notational simplicity, we will let $s_1$ and $s_2$ be two copies of strategy $s$. Then, $v_{s}(s) = v_{s_1}(s_2) = v_{s_2}(s_1)$. By definition, we have
  \begin{equation*}
    v_{s_1}(s_2) = \sum \pi_{c_1,c_2} \cdot r(c_1,c_2)
  \end{equation*}
  and
  \begin{equation*}
    v_{s_2}(s_1) = \sum \pi_{c_2,c_1} \cdot r(c_2,c_1).
  \end{equation*}
  Note that $\pi_{c_1,c_2}$ and $\pi_{c_2,c_1}$ refer to the same state, so we thus have \begin{equation*}
    v_{s_1}(s_2) + v_{s_2}(s_1) = \sum \pi_{c_1,c_2} \cdot (r(c_1,c_2) + r(c_2,c_1))
  \end{equation*}
  which implies that \begin{equation*}
    v_s(s) = \sum \left( \pi_{c_1,c_2} \cdot \frac{r(c_1,c_2) + r(c_2,c_1)}{2} \right).
  \end{equation*}
  Now, note that $r(c_1,c_2) + r(c_2,c_1) \in \{R + R, S + T, T+S, P + P\}$. Since $P < R$ and $T + S < 2R$, we thus find that \begin{equation*}
    v_s(s) \leq \sum \pi_{c_1,c_2} \cdot R = R \sum \pi_{c_1,c_2} = R,
  \end{equation*}
  as desired.
\end{proof}

\subsection{Evolutionary Stability Implies Utilitarianism}

  The following proof is relatively involved, and we believe that a simpler proof exists, but haven't been able to find one.

    \begin{proof}[Proof of \cref{evolutionarystable1}]
      Suppose that the strategy $s_1$ is such that it is \textit{not} true that \begin{equation*}
        \lim_{p \to 0 } v_{s_1}(s_1) = R
      \end{equation*}
      By \cref{limitvexists} and \cref{neverbetterthanr}, this assumption implies that the limit is strictly less than $R$. Define $\gamma = \lim_{p \to 0} v_{s_1}(s_1)$. Then,
      \begin{equation*}
        \gamma < R.
      \end{equation*}

@@

      The underlying idea is to create $s_2$ such that $s_1$ can see no difference between itself and $s_2$, while $s_2$, on the other hand, can. In that case, we would have that $v_{s_1}(s_2) = v_{s_2}(s_1) = v_{s_1}(s_1)$, and could construct $s_2$ such that it always cooperates when it recognizes itself, thereby yielding $v_{s_2}(s_2) = R$. This would give $s_2$ a higher fitness than $s_1$. The rest of this proof executes this plan in detail.

      We create the strategy $s_2$ as follows. First, we copy all of $s_1$ into $s_2$. Let $\mathcal{C}_1$ be the set of
       absorbing strongly connected components of $s_1$. The key idea, now, is to replace each original absorbing strongly connected component $C_1 \in \mathcal{C}_1$ with a new absorbing component $C_2$, which has the capability of self identifying.

      We now construct $C_2$, given $C_1$. \Cref{c2flowchart} shows the high-level construction of $C_2$. All of the steps succeed with probability $1 - O(p)$. The first step makes sure that $C_2$ does not deviate from $s_1$ at all, until $s_1$ has reached an absorbing strongly connected component. Once $s_1$ is in an absorbing strongly connected component, we already know that the time average distribution does not depend on the particular state in $s_1$, which means that even if $s_1$ now ``figures out'' that it is not playing against itself anymore, there is nothing it can do about it. The next step makes sure that, if $s_2$ is playing against itself, it is in sync; i.e., with probability $1 - O(p)$ they will both copies of $s_2$ will be in the same state after this step. The third step now figures out what action $s_1$ would take at some large finite time $T$, and then outputs the exact opposite action at time $T$. At that point, if its opponent outputs $s_1$'s expected action, it transitions into the absorbing strongly connected component $C_1$, but if its opponent outputs the opposite of that action, it has successfully recognized itself and enters an always cooperating state.

      \begin{figure}
        \centering
        \begin{tikzpicture}[node distance=0.9cm,initial text=]
          \node[elliptic state, initial, initial where=above] (c_0) {1. Wait until $s_1$ is in an absorbing SCC, while simulating $C_1$.};
          \node[elliptic state] (c_1) [below=of c_0] {2. Sync $s_2$.};
          \node[elliptic state] (c_3) [below=of c_1] {3. Figure out what action that $s_1$ will take right after this.};
          \node[state] (c_4) [below left=of c_3] {$C$};
          \node[state] (c_5) [below right=of c_3] {$D$};
          \node[state] (c_6) [below=of c_5] {$C$};
          \node[state] (c_7) [below=of c_4] {$C_1$};

          \path[->] (c_0) edge (c_1);
          \path[->] (c_1) edge (c_3);
          \path[->] (c_3) edge node [above left] {$s_1$ will take $D$} (c_4);
          \path[->] (c_3) edge node [above right] {$s_1$ will take $C$} (c_5);
          \path[->] (c_4) edge node [below, pos=0.1] {$C$} (c_6);
          \path[->] (c_5) edge node [right] {$D$} (c_6);
          \path[->] (c_4) edge node [left] {$D$} (c_7);
          \path[->] (c_5) edge node [below, pos=0.1] {$C$} (c_7);
          \path[->] (c_6) edge [loop right] (c_6);
          % \path[->] (c_0) edge node [above right] {$\bar{\alpha}$} (c_1);
          % \path[->] (c_1) edge [loop right] node [right] {$C,D$} ();
          % \path[->] (c_0) edge node [above left] {$\alpha$} (c_prime);
          % \path[->] (c) edge node [below left] {$\alpha$} (c_prime);
        \end{tikzpicture}
        \caption{High level construction of $C_2$, the absorbing component replacing $C_1$ when creating $s_2$ in the proof of \cref{evolutionarystable1}. Note that $C_2$ contains exactly 2 absorbing strongly connected components.}
        \label{c2flowchart}
      \end{figure}

      This concludes the construction of $s_2$. We now want to prove that this $s_2$ can in fact invade $s_1$. To do that, we will first assume that the below 3 claims are correct, i.e., that the construction is possible and works as specified, and finish the proof of our theorem using those assumptions. Then, we will prove the 3 claims.

      \begin{claim}
        \label{claimcanwaitfors1}
        We can construct a non-absorbing component with indistinguishable output from the component $C_1$, such that when we leave the component, $s_1$ will be in an absorbing strongly connected component with probability $1 - O(p)$.
      \end{claim}

@@

        That $v_{s_1}(s_1) = \gamma + O(p)$ follows by our definition of $\gamma$.

        Consider first the case of $s_1$ playing against $s_2$. By \cref{claimcanwaitfors1}, with probability $1 - O(p)$, $s_2$ is indistinguishable from $s_1$ until $s_1$ reaches an absorbing strongly connected component $C_1'$. This means that the probability for reaching the absorbing component $(C_1', C_2)$ in the $s_1$-$s_2$ Markov chain, is up to a factor of $1 - O(p)$ the same as if we hadn't replaced $C_1$ by $C_2$, which is just the probability of reaching the absorbing component $(C_1', C_1)$ in the $s_1$-$s_1$ Markov chain. Thus, 
        \begin{multline*}
          P(\text{$s_1$-$s_2$ chain ends up in $(C_1', C_2)$}) \\ = (1 - O(p)) P(\text{$s_1$-$s_1$ chain ends up in $(C_1', C_1)$})
        \end{multline*}
        Now, by \cref{claimcanfigureout}, the probability that $s_2$ enters the absorbing strongly connected component $C_1$ after having gotten to $C_2$ is $1 - O(p)$, and that it enters the always cooperating component $C_c$ is $O(p)$. Thus,
        \begin{align*}
          P(\text{$s_1$-$s_2$ chain ends up in $(C_1',C_1)$}) &= P(\text{$s_1$-$s_1$ chain ends up in $(C_1',C_1)$}) + O(p) \\
          P(\text{$s_1$-$s_2$ chain ends up in $(C_1',C_c)$}) &= O(p)
        \end{align*}
        That is, when $s_1$ plays against $s_2$, the absorbing strongly connected components are mostly the same, with mostly the same probabilities. 
        Now, we can calculate $\tau$, the time average distribution of the $s_1$-$s_2$ Markov chain:

@@

      Given \cref{claimpayoffs}, we simply compute $F(s_2) - F(s_1)$, which we want to show is greater than 0.
      \begin{align*}
        F(s_2) - F(s_1) &= \\
        &= (1 - \epsilon) \cdot v_{s_2}(s_1) + \epsilon \cdot v_{s_2}(s_2) - (1 - \epsilon) \cdot v_{s_1}(s_1) - \epsilon \cdot v_{s_1}(s_2) \\
        &= (1 - \epsilon) (\gamma - O(p)) + \epsilon (R - O(p)) - (1-\epsilon) \gamma - \epsilon (\gamma + O(p)) \\
        &\leq \epsilon (R - \gamma) + O(p)
      \end{align*}

>>>>

\begin{definition}
  \label{payofftimeaverage}
  Let $r(c_1, c_2)$ refer to the reward that $s_1$ gets when $s_1$ takes the action in state $c_1$ and $s_2$ takes the action in state $c_2$. Then, the \textit{payoff that $s_1$ gets when playing against $s_2$} is
  \begin{equation*}
    v_{s_1}(s_2) = \sum_{(c_1,c_2)} \pi_{c_1,c_2} \cdot r(c_1, c_2),
  \end{equation*}
  where the sum is taken over all states $(c_1,c_2)$ in the $s_1$-$s_2$ Markov chain.
\end{definition}

For notational convenience, we may also make $r(c_1, c_2)$ into a vector, denoted by $r$, and write this as the dot product \begin{equation*}
  v_{s_1}(s_2) = \pi \cdot r.
\end{equation*}

@@

We can now state our results! Together, the following theorem and conjecture imply that in the setup described here, mutual cooperation arises as the only stable choice.

\begin{theorem}
  \label{evolutionarystable1}
  Suppose that a strategy $s_1$ is evolutionarily stable. Then $\lim_{p \to 0} v_{s_1}(s_1) = R$.
\end{theorem}

\begin{conjecture}
  \label{pavlovtheorem}
  Suppose that $2R > T + P$. Then, the Pavlov strategy, depicted in \cref{pavlovfigure}, is evolutionarily stable.
\end{conjecture}

  \path[->] (s_0) edge [loop above] node {$C$} ();
  \path[->] (s_0) edge [bend left] node [above] {$D$} (s_1);
  \path[->] (s_1) edge [loop above] node {$C$} ();
  \path[->] (s_1) edge [bend left] node [below] {$D$} (s_0);
\end{tikzpicture}
  \centering
  \caption{The Pavlov strategy. Similar to but not the same as the Tit-for-tat strategy.}
  \label{pavlovfigure}
\end{figure}

@@

\begin{lemma}
  \label{timeaverageisstationary}
  The time average distribution $\pi^{(a,b)}$, for any starting state $(a,b)$, is a stationary distribution of the Markov chain. That is, if $M$ is the transition matrix of the Markov chain, we have $M \pi^{(a,b)} = \pi^{(a,b)}$.
\end{lemma}

@@

\begin{lemma}
  \label{lemmaabsorbinghasuniquetimeaverage}
  An absorbing strongly connected component has a unique time average distribution, i.e., the time average distribution does not depend on the start state.
\end{lemma}

\begin{proof}
  It is well known that a strongly connected (also known as irreducible) Markov chain has a unique stationary distribution. Since the time average distribution is stationary by \cref{timeaverageisstationary}, it thus also has to be unique.
\end{proof}

\begin{lemma}
  \label{timeaveragedistributiondecomposition}
  Let $\mathcal{A}$ be the set of absorbing strongly connected components of the $s_1$-$s_2$ Markov chain. For every $S \in \mathcal{A}$, let $\pi^{(S)}$ be its unique time average distribution. Then, for some probabilities $p_{S}$ with $\sum_{S \in \mathcal{A}} p_{S} = 1$, corresponding to the time average probabilities of ending up in the absorbing strongly connected component $S$, we have \begin{equation*}
    \pi = \sum_{S \in \mathcal{A}} p_{S} \cdot \pi^{(S)}.
  \end{equation*}
\end{lemma}

@@

\begin{lemma}
  \label{absorbingstronglyconnectedcomponentscartesianproduct}
  Let $\mathcal{A}_1$ be the set of absorbing strongly connected components of $s_1$, and similarly, let $\mathcal{A}_2$ be the set of absorbing strongly connected components of $s_2$. If $\mathcal{A}$ is the set of absorbing strongly connected components of the $s_1$-$s_2$ Markov chain, then 
  \begin{equation*}
    \mathcal{A} = \{H \times K \mid H \in \mathcal{A}_1 \text{ and } K \in \mathcal{A}_2\},
  \end{equation*}
  where $A \times B$ is the cartesian product $A \times B = \{(a, b) \mid a \in A \text{ and } b \in B\}$.
\end{lemma}

Now that we know more about the time average distribution, we are also interested in proving that the payoff function behaves nicely.

@@

\begin{lemma}
  \label{neverbetterthanr}
  For any strategy $s$,
  \begin{equation*}
    v_{s}(s) \leq R
  \end{equation*}
\end{lemma}
\begin{proof}
  For notational simplicity, we will let $s_1$ and $s_2$ be two copies of strategy $s$. Then, $v_{s}(s) = v_{s_1}(s_2) = v_{s_2}(s_1)$. By definition, we have
  \begin{equation*}
    v_{s_1}(s_2) = \sum \pi_{c_1,c_2} \cdot r(c_1, c_2)
  \end{equation*}
  and
  \begin{equation*}
    v_{s_2}(s_1) = \sum \pi_{c_2,c_1} \cdot r(c_2, c_1).
  \end{equation*}
  Note that $\pi_{c_1,c_2}$ and $\pi_{c_2,c_1}$ refer to the same state, so we thus have \begin{equation*}
    v_{s_1}(s_2) + v_{s_2}(s_1) = \sum \pi_{c_1,c_2} \cdot (r(c_1,c_2) + r(c_2,c_1))
  \end{equation*}
  which implies that \begin{equation*}
    v_s(s) = \sum \left( \pi_{c_1,c_2} \cdot \frac{r(c_1,c_2) + r(c_2,c_1)}{2} \right).
  \end{equation*}
  Now, note that $r(c_1,c_2) + r(c_2,c_1) \in \{R + R, S + T, T+S, P + P\}$. Since $P < R$ and $T + S < 2R$, we thus find that \begin{equation*}
    v_s(s) \leq \sum \pi_{c_1,c_2} \cdot R = R \sum \pi_{c_1,c_2} = R,
  \end{equation*}
  as desired.
\end{proof}

\subsection{Evolutionary Stability Requires Cooperation}

  We are now finally ready to prove that to be evolutionarily stable, a strategy needs to cooperate with a clone of itself.

    \begin{proof}[Proof of \cref{evolutionarystable1}]
      Suppose that the strategy $s_1$ is such that it is \textit{not} true that \begin{equation*}
        \lim_{p \to 0 } v_{s_1}(s_1) = R.
      \end{equation*}
      By \cref{limitvexists} and \cref{neverbetterthanr}, this assumption implies that the limit is strictly less than $R$. Define $\gamma = \lim_{p \to 0} v_{s_1}(s_1)$. Then,
      \begin{equation*}
        \gamma < R.
      \end{equation*}

@@

      The underlying idea is to construct $s_2$ such that $s_1$ can see no difference between itself and $s_2$, while $s_2$, on the other hand, can. If we succeed in doing so, we will have that $v_{s_1}(s_2) = v_{s_2}(s_1) = v_{s_1}(s_1)$, and can construct $s_2$ such that it always cooperates when it recognizes itself, thereby yielding $v_{s_2}(s_2) = R$. This would give $s_2$ a higher fitness than $s_1$. The rest of this proof executes this plan in detail.

      We create the strategy $s_2$ as follows. First, we copy all of $s_1$ into $s_2$. Let $\mathcal{A}_1$ be the set of
       absorbing strongly connected components of $s_1$. The key idea, now, is to replace each original absorbing strongly connected component $H \in \mathcal{A}_1$ with a new absorbing component $K_H$, which has the capability of identifying itself.

      We now construct a $K_H$ for each $H$. \Cref{c2flowchart} shows the high-level construction of $K_H$.
       All of the steps succeed with probability $1 - O(p)$. The first step makes sure that $K_H$ does not deviate from $s_1$ at all
        until $s_1$ has reached an absorbing strongly connected component. 
       Once $s_1$ is in an absorbing strongly connected component, \cref{lemmaabsorbinghasuniquetimeaverage} tells us that the time average distribution does not depend on the particular start state in that component, which means that even if $s_1$ after this point ``figures out'' that it is not playing against itself anymore, there is nothing it can do about it (since it also cannot escape the component). 
      The second step in the construction of $K_H$ makes sure that if $s_2$ is playing against itself, it is in sync with its clone; that is, with probability $1 - O(p)$, both copies of $s_2$ will be in the exact same state after the second step. 
      The third step now figures out what action $s_1$ would take at some large finite time $T$. 
      Then, $K_H$ outputs the exact opposite action at time $T$. 
      At that point, if its opponent outputs $s_1$'s expected action, it transitions into the absorbing strongly connected component $H_\text{copy}$, which is just an exact copy of $H$, but if its opponent outputs the opposite of that action, it has successfully recognized itself and enters an always cooperating state.

      \begin{figure}
        \centering
        \begin{tikzpicture}[node distance=0.9cm,initial text=]
          \node[elliptic state, initial, initial where=above] (c_0) {1. Wait until $s_1$ is in an absorbing SCC, while simulating $H$.};
          \node[elliptic state] (c_1) [below=of c_0] {2. Sync $s_2$.};
          \node[elliptic state] (c_3) [below=of c_1] {3. Figure out what action that $s_1$ will take right after this.};
          \node[state] (c_4) [below left=of c_3] {$C$};
          \node[state] (c_5) [below right=of c_3] {$D$};
          \node[state] (c_6) [below=of c_5] {$C$};
          \node[elliptic state] (c_7) [below=of c_4] {$H_\text{copy}$ \\(an exact copy of $H$)};

          \path[->] (c_0) edge (c_1);
          \path[->] (c_1) edge (c_3);
          \path[->] (c_3) edge node [above left] {$s_1$ will take $D$} (c_4);
          \path[->] (c_3) edge node [above right] {$s_1$ will take $C$} (c_5);
          \path[->] (c_4) edge node [below, pos=0.1] {$C$} (c_6);
          \path[->] (c_5) edge node [right] {$D$} (c_6);
          \path[->] (c_4) edge node [left] {$D$} (c_7);
          \path[->] (c_5) edge node [below, pos=0.1] {$C$} (c_7);
          \path[->] (c_6) edge [loop right] (c_6);
          % \path[->] (c_0) edge node [above right] {$\bar{\alpha}$} (c_1);
          % \path[->] (c_1) edge [loop right] node [right] {$C,D$} ();
          % \path[->] (c_0) edge node [above left] {$\alpha$} (c_prime);
          % \path[->] (c) edge node [below left] {$\alpha$} (c_prime);
        \end{tikzpicture}
        \caption{High level construction of $K_H$, the absorbing component replacing $H$ when creating $s_2$ in the proof of \cref{evolutionarystable1}. Note that $K_H$ contains exactly 2 absorbing strongly connected components.}
        \label{c2flowchart}
      \end{figure}

      This concludes the high-level construction of $s_2$. We now want to prove that this $s_2$ can in fact invade $s_1$. To do that, we will first assume that the below 3 claims are correct, i.e., that the construction is possible and works as specified, and then finish the proof of our theorem using those assumptions. Once that's done, we will prove the 3 claims.

      \begin{claim}
        \label{claimcanwaitfors1}
        We can construct a non-absorbing component with behavior indistinguishable from the behavior of component $H$, such that when we leave the component, $s_1$ will be in an absorbing strongly connected component with probability $1 - O(p)$.
      \end{claim}

@@

        By our definition of $\gamma$, we have that $v_{s_1}(s_1) = \gamma + O(p)$.

        Consider now the case of $s_1$ playing against $s_2$. Suppose that $s_2$ ends up in the absorbing component $K_H$. By \cref{claimcanwaitfors1}, with probability $1 - O(p)$, $s_2$ is indistinguishable from $s_1$ until $s_1$ also reaches an absorbing strongly connected component, which we call $H'$. This means that the probability for reaching the absorbing component $(C_1', C_2)$ in the $s_1$-$s_2$ Markov chain, is up to a factor of $1 - O(p)$ the same as if we hadn't replaced $C_1$ by $C_2$, which is just the probability of reaching the absorbing component $(C_1', C_1)$ in the $s_1$-$s_1$ Markov chain. Thus, 
        \begin{multline*}
          P(\text{$s_1$-$s_2$ chain ends up in $(C_1', C_2)$}) \\ = (1 - O(p)) P(\text{$s_1$-$s_1$ chain ends up in $(C_1', C_1)$})
        \end{multline*}
        Now, by \cref{claimcanfigureout}, the probability that $s_2$ enters the absorbing strongly connected component $C_1$ after having gotten to $C_2$ is $1 - O(p)$, and that it enters the always cooperating component $C_c$ is $O(p)$. Thus,
        \begin{align*}
          P(\text{$s_1$-$s_2$ chain ends up in $(C_1',C_1)$}) &= P(\text{$s_1$-$s_1$ chain ends up in $(C_1',C_1)$}) + O(p) \\
          P(\text{$s_1$-$s_2$ chain ends up in $(C_1',C_c)$}) &= O(p)
        \end{align*}
        That is, when $s_1$ plays against $s_2$, the absorbing strongly connected components are mostly the same, with mostly the same probabilities. 
        Now, we can calculate $\tau$, the time average distribution of the $s_1$-$s_2$ Markov chain:

@@

      Given \cref{claimpayoffs}, we simply compute $F(s_2) - F(s_1)$, which we want to show is greater than 0.
      \begin{align*}
        F(s_2) - F(s_1) &= \\
        &= (1 - \epsilon) \cdot v_{s_2}(s_1) + \epsilon \cdot v_{s_2}(s_2) - (1 - \epsilon) \cdot v_{s_1}(s_1) - \epsilon \cdot v_{s_1}(s_2) \\
        &= (1 - \epsilon) (\gamma - O(p)) + \epsilon (R - O(p)) - (1-\epsilon) \gamma - \epsilon (\gamma + O(p)) \\
        &\geq \epsilon (R - \gamma) - O(p)
      \end{align*}
